1.3 Meet R - R Practice

### 2019-09-06 content/r/03-r-practice.Rmd
Fixed link in R practice 1.3 html answers

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```
- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/r/03-r-practice.pdf)
- [<i class="fas fa-file-pdf"></i> `Answer Key`](/r/03-r-practice-answers.pdf)
- [<i class="fas fa-registered"></i> `R Script`](/r/03-r-practice-answers.R)

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```
- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/r/03-r-practice.pdf)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/r/03-r-practice-answers.html)
- [<i class="fas fa-file-pdf"></i> `Answer Key (PDF)`](/r/03-r-practice-answers-pdf.pdf)
- [<i class="fas fa-registered"></i> `R Script`](/r/03-r-practice-answers.R)
